Timely Object Recognition

### 2012-08-03 writeups/nips12/rebuttal.txt

All reviewers noted the significance of our "refreshingly new" view on performing and evaluating object detection, and recognized that we open interesting research avenues with convincing results.
As Reviewer 6 writes, we introduce a new ``timeliness'' AP vs. Time measure of detection performance, and use a reinforcement learning approach to optimize it.

The reviewer's main uncertainties about our method concern the reward function:
1) that it assumes that the measure is non-decreasing;
2) that it depends on a deadline time.

The first concern is not valid, as the definition of the reward can absolutely handle decreasing AP vs. Time: it simply produces negative rewards, which pose no problem to our learning approach.

Regarding the second concern, we note in the abstract that our goal is Anytime performance **between a start time and a deadline**.
Figure 3b illustrates a situation in which the deadline plays an important role: the very last possible action is illustrated as a choice between a solid green line and a dashed red line.
The green line is for an action that obtains a lower AP but finishes prior to deadline; the red line is for an action that obtains a higher AP but finishes after deadline.
The system should be able to learn to take the ``green'' action; this is why our reward function depends on a deadline time.

We appreciate the reviewer's valuable suggestion for a modification to the reward function, and agree that it would be helpful to provide more exposition here.

Regarding the reviewer's additional comments:
- Entropy: that is correct;
- Class correlations: that is correct, which is why we use an MRF model for inference: it is able to learn additional correlations;
- Actions: as we write, we report runtimes for a specific combination of software implementation and hardware; the details are not as important as the general approach used, as our learning is agnostic to the performances of the system components
We use the original MATLAB implementation of GIST by Torralba, which takes about a quarter of the time of the cascaded DPM implementation by Felzenswalb.

Reviewer 8 considers our approach to be interesting and new, but believes that the work of [18] is a close analog.
We disagree; while [18] uses a similar evaluation, they formulate a very specific system for object categorization using local features.
In contrast, we develop a general framework for optimizing object detection, using different detectors and classifiers.
The closest work to ours is [19], but it deals with classification and not detection, and does not learn non-greedy policies.

In fact, the reviewer's questions regarding the basics of Figures 1 and 2 raise concerns about their understanding of our approach.
Figure 1 shows the execution of our system over time, as different actions (classification and detection) are performed in sequence, results are obtained, and inference is performed in the MRF.
Figure 2 shows the weights learned by greedy learning and reinforcement learning on the features that represent the state of the system; the differences are illustrative of the desired properties of the reinforecement learning approach.
Regarding fairness, we note that we report multiple time bounds exactly for that reason.

Reviewer 5 provides helpful comments that we appreciate and would love to further discuss in another venue due to space constraints of this rebuttal.
We sincerely appreciate all the reviewers' effort in providing very helpful comments on our paper!

### 2012-11-02 writeups/nips12/introduction.tex
final polish
final
working on nips final and reorganizing slides into deadline folders

In most real-world applications of object recognition, performance is time-sensitive and inherently tied to the many-class nature of the world.
In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
In large-scale detection systems (e.g. image search), results need to be obtained quickly per image as the number of items to process is constantly growing.
In these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.

@@

We propose a new \emph{timeliness} measure of performance vs. time (shown in Figure~\ref{fig:figure1}), and present a method based on reinforcement learning that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
We are able to obtain better performance than baselines when there is less time available than is needed to run all detectors.

>>>>

In real-world applications of visual object recognition, performance is time-sensitive.% and inherently tied to the many-class nature of the world.
In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection, if the robot is to usefully interact with humans.
In large-scale detection systems (e.g. image search), results need to be obtained quickly per image as the number of items to process is constantly growing.
In these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.

@@

We propose a new \emph{timeliness} measure of performance vs. time (shown in Figure~\ref{fig:figure1}), and present a method based on reinforcement learning that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
We are able to obtain better performance than all baselines when there is less time available than is needed to exhaustively run all detectors.
